\input{./src/main.sty}
% Additional SI unit for Fahrenheit
\DeclareSIUnit\fahrenheit{\degree F}

\begin{document}

% Include title page
\input{./src/titlepage.tex}

\pagebreak

\begin{enumerate}
  \item After careful synthesis, you finally manage to create a new
    substance (call it ‘A’) that maintains a
    liquid phase over a wide range of temperatures and will mix with
    water on warm days but is immiscible
    with water on colder days. The mixture of A and water seems to
    obey the regular solution model to
    an absurd degree. Before publishing your results, you hope to
    characterize binary mixtures of A and
    water in terms of the regular solution model through a series of
    experiments.

    \begin{enumerate}[(a.)]
      \item In preparation, you wish to recall the relationship
        between equilibrium volume fraction and
        the interaction parameter $\chi$. Starting from the mixing free
        energy, derive this relationship.
      \item  Without bothering to measure the initial volume fraction
        of A, you start by cooling the mixture to $T =
        \SI{50}{\degree F}$, observing phase
        separation. Carefully
        drawing a sample from the A-rich phase, you
        then determine that it has a volume fraction of $\phi_A = 0.8$.
        What is the value of $\chi$ that this corresponds
        to?
      \item In a separate experiment, you prepare a mixture, this
        time taking care to record a volume
        fraction $\phi_A^{(0)} = 0.6$, and place it in your lab
        refrigerator, cooling it to
        $T = \SI{35}{\degree F}$ . You notice an
        % \ul{almost complete separation} of A from water.
        Thinking that you
        might have difficulty measuring the
        possibly trace amounts of water in the A-rich phase, you
        instead note that the A-rich phase occupies
        about \SI{62}{\percent} of the container. Use this
        information to determine
        \si{\percent} the volume fraction of the A-rich phase.
      \item he interaction parameter can be expressed as a function
        of temperature as $\chi = \frac{A}{T} + B$,
        where $T$ is measured in Kelvin and $A$ and $B$ are material
        constants. Using the data obtained from your two
        experiments, determine $A$ and $B$.
      \item Using what you have learned, determine the \textit{upper critical
        solution temperature (UCST)} – the
        temperature above which A and water are miscible for all compositions.
    \end{enumerate}

  \item You have found that the partial molar volume of component 1
    of a two-component system is given
    by

    \begin{equation}
      \Delta \overline V_1 = 2aX_1X_2^2
    \end{equation}

    where $a = \SI{2.7166}{\centi\meter\cubed\per\mole}$

    \begin{enumerate}[(a.)]
      \item Determine an equation for the change in partial molar
        volume of component 2 during mixing
        as a function of composition.
      \item Determine an equation for the total volume change during
        mixing as a function of composition.
      \item Calculate the total volume change of the mixture, the
        partial molar volume change of component 1, and the partial
        molar volume change of component 2
        (three separate numerical answers) when
        \SI{75}{\mole} of component 1 are mixed with \SI{25}{\mole}
        of component 2.
      \item GRAPHICALLY (i.e., you will need to plot something)
        verify the partial molar volume change
        of component 1 that you calculated in part (c). You can
        estimate your answer for this part.
    \end{enumerate}

  \item Consider a binary phase containing the alloying elements A
    and B, which follows a subregular
    solution model with the following mixing parameters:

    \begin{align*}
      \omega_A &= \SI{10500}{\joule\per\mole} \\
      \omega_B &= \SI{-3000}{\joule\per\mole}
    \end{align*}

    You can assume that both A and B have references states
    consistent with the phase being plotted.

    \begin{enumerate}[(a.)]
      \item On the same plot, plot $T\Delta S_{\text{mix}}$, $\Delta
        H_{\text{mix}}$, and
        $\Delta G_{\text{mix}}$ for this
        phase at \SI{500}{\kelvin} over a compositional range of $X_B
        = 0$ to $X_B = 1$.
      \item On a new plot, plot that same three curves at
        \SI{5000}{\kelvin} over
        the same compositional range.
        Describe what you see in this plot and how entropy and
        enthalpy play into the overall Gibbs free
        energy of mixing.
      \item Using your plot from part (a), graphically determine the
        activity coefficient of B in an alloy
        containing \SI{60}{at\percent} B at \SI{500}{\kelvin}.
    \end{enumerate}

\end{enumerate}

% \section*{Supporting code:}
% \inputminted{julia}{./calculations/src/calculations.jl}

\end{document}
